Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-22 paper/ms.tex
adding vdp to acks

\keywords{%
% methods: data analysis
% ---
% methods: statistical
% ---
% catalogs
% ---
% planetary systems
% ---
% stars: statistics
}

@@

\acknowledgments
It is a pleasure to thank
Megan Bedell,
Will Farr,
Sam Grunblatt,
David W.\ Hogg, and
Dan Huber
for helpful contributions to the ideas and code presented here.

>>>>

\keywords{%
 methods: data analysis
 ---
 methods: data analysis
 ---
 methods: statistical
 ---
 asteroseismology
 ---
 stars: rotation
 ---
 planetary systems
}

@@

\acknowledgments
It is a pleasure to thank
Megan Bedell,
Will Farr,
Sam Grunblatt,
David W.\ Hogg,
Dan Huber, and
Jake VanderPlas
for helpful contributions to the ideas and code presented here.
